Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-27 reanalysis-4-outcome_analysis.qmd
contrasts

scenarios$baseline_VA_logMAR <- weighted_means["baseline_VA_logMAR"]
scenarios$age_cat <- get_mode(imp_data$age_cat, imp_data$weights)
scenarios$gender_cat <- get_mode(imp_data$gender_cat, imp_data$weights)
scenarios$race_ethnic_cat <- get_mode(imp_data$race_ethnic_cat, imp_data$weights)
scenarios$insurance_cat <- get_mode(imp_data$insurance_cat, imp_data$weights)
scenarios$CCI <- round(weighted_means["CCI"])
scenarios$DCSI <- round(weighted_means["DCSI"])
scenarios$glaucoma_bef_hitplus_cat <- 0
scenarios$otherretina_bef_hitplus_cat <- 0
scenarios$catsurg_before_hitplus_cat <- 0

>>>>

# Set continuous variables
scenarios$baseline_VA_logMAR <- as.numeric(weighted_means["baseline_VA_logMAR"])
scenarios$CCI <- round(as.numeric(weighted_means["CCI"]))
scenarios$DCSI <- round(as.numeric(weighted_means["DCSI"]))

# Set categorical variables as factors with proper levels
scenarios$age_cat <- factor(get_mode(imp_data$age_cat, imp_data$weights), 
                            levels = levels(imp_data$age_cat))
scenarios$gender_cat <- factor(get_mode(imp_data$gender_cat, imp_data$weights),
                               levels = levels(imp_data$gender_cat))
scenarios$race_ethnic_cat <- factor(get_mode(imp_data$race_ethnic_cat, imp_data$weights),
                                    levels = levels(imp_data$race_ethnic_cat))
scenarios$insurance_cat <- factor(get_mode(imp_data$insurance_cat, imp_data$weights),
                                  levels = levels(imp_data$insurance_cat))

# Set binary factors
scenarios$glaucoma_bef_hitplus_cat <- factor(0, levels = c(0, 1))
scenarios$otherretina_bef_hitplus_cat <- factor(0, levels = c(0, 1))
scenarios$catsurg_before_hitplus_cat <- factor(0, levels = levels(imp_data$catsurg_before_hitplus_cat))

# Ensure dr_severity and any_treatment are factors
scenarios$dr_severity <- factor(scenarios$dr_severity, levels = c("No_DR", "NPDR", "PDR"))
scenarios$any_treatment <- factor(scenarios$any_treatment, levels = c(0, 1))
